\chapter{大洪水 Leo，Stefanie，慧娟，慧洁}

\section{中文经文 - 挪亚方舟和大洪水}
\subsection{大洪水的原因 6:9-13/7:1-4}

挪亚的后代记在下面。挪亚是个义人，在当时的世代是个完全人。挪亚与神同行。挪亚生了三个儿子，就是闪、含、雅弗。世界在神面前败坏，地上满了强暴。神观看世界，见是败坏了，凡有血气的人，在地上都败坏了行为。神就对挪亚说：“凡有血气的人，他的尽头已经来到我面前，因为地上满了他们的强暴。我要把他们和地一并毁灭。\\

耶和华对挪亚说：“你和你的全家都要进入方舟，因为在这世代中，我见你在我面前是义人。凡洁净的畜类，你要带七公七母，不洁净的畜类，你要带一公一母，空中的飞鸟也要带七公七母，可以留种，活在全地上。因为再过七天，我要降雨在地上四十昼夜，把我所造的各种活物都从地上除灭。” 挪亚就遵着耶和华所吩咐的行了。\\

问题：
\begin{itemize}
\item 神为什么要用洪水毁灭世界（请用蓝色笔标注）？
\item 神为什么把毁灭世界的计划只透露给挪亚，挪亚有什么特征（请用红色笔标注）？
\item 神提前几天告诉挪亚要发大洪水的消息的？
\end{itemize}
\\

\subsection{大洪水的过程}
\subsubsection{挪亚入方舟 7:6-16}
6 当洪水泛滥在地上的时候，挪亚整六百岁。 7 挪亚就同他的妻和儿子、儿妇，都进入方舟，躲避洪水。 8 洁净的畜类和不洁净的畜类，飞鸟并地上一切的昆虫， 9 都是一对一对的，有公有母，到挪亚那里进入方舟，正如神所吩咐挪亚的。 10 过了那七天，洪水泛滥在地上。 11 当挪亚六百岁，二月十七日那一天，大渊的泉源都裂开了，天上的窗户也敞开了， 12 四十昼夜降大雨在地上。13 正当那日，挪亚和他三个儿子闪、含、雅弗，并挪亚的妻子和三个儿妇，都进入方舟。 14 他们和百兽各从其类，一切牲畜各从其类，爬在地上的昆虫各从其类，一切禽鸟各从其类，都进入方舟。 15 凡有血肉、有气息的活物，都一对一对地到挪亚那里，进入方舟。 16 凡有血肉进入方舟的，都是有公有母，正如神所吩咐挪亚的。耶和华就把他关在方舟里头。\\

问题：
\begin{itemize}
\item 大洪水在哪天发生的？
\item 在这么短的时间内，挪亚如何召聚所有要带入方舟的动物的？
\item  挪亚方舟里的住客都有谁？为什么没有鱼?
\end{itemize}

\newpage
\subsubsection{挪亚出方舟 7:23-24/8:4-19}
23 凡地上各类的活物，连人带牲畜、昆虫，以及空中的飞鸟，都从地上除灭了，只留下挪亚和那些与他同在方舟里的。4 七月十七日，方舟停在亚拉腊山上。 5 水又渐消，到十月初一日，山顶都现出来了。过了四十天，挪亚开了方舟的窗户， 7 放出一只乌鸦去。那乌鸦飞来飞去，直到地上的水都干了。 8 他又放出一只鸽子去，要看看水从地上退了没有。 9 但遍地上都是水，鸽子找不着落脚之地，就回到方舟挪亚那里，挪亚伸手把鸽子接进方舟来。 10 他又等了七天，再把鸽子从方舟放出去。 11 到了晚上，鸽子回到他那里，嘴里叼着一个新拧下来的橄榄叶子，挪亚就知道地上的水退了。 12 他又等了七天，放出鸽子去，鸽子就不再回来了。13 到挪亚六百零一岁，正月初一日，地上的水都干了。挪亚撤去方舟的盖观看，便见地面上干了。 14 到了二月二十七日，地就都干了。\\
\\
神对挪亚说： 16 “你和你的妻子、儿子、儿妇都可以出方舟。 17 在你那里凡有血肉的活物，就是飞鸟、牲畜和一切爬在地上的昆虫，都要带出来，叫它在地上多多滋生，大大兴旺。” 18 于是挪亚和他的妻子、儿子、儿妇都出来了。 19 一切走兽、昆虫、飞鸟和地上所有的动物，各从其类，也都出了方舟。\\

问题：
\begin{itemize}
\item 方舟停在了什么山？
\item 挪亚一家在方舟里呆了多长时间？你觉得他们在方舟里会做什么？
\item 关于挪亚出方舟，哪个描述是对的？
\begin{itemize}
\item A，挪亚撤去方舟的盖观看，便见地面上干了， 他就带领全家出了方舟
\item B，神吩咐挪亚说：  “你和你的妻子、儿子、儿妇都可以出方舟“， 挪亚就出了方舟
\end{itemize}
\item 思考：在挪亚造方舟，入方舟，出方舟的过程中，我们从挪亚学习到什么？
\end{itemize}


\subsection{大洪水之后}

\subsubsection{挪亚筑坛献祭 8:20-22}
挪亚为耶和华筑了一座坛，拿各类洁净的牲畜、飞鸟献在坛上为燔祭。 21 耶和华闻那馨香之气，就心里说：“我不再因人的缘故咒诅地（人从小时心里怀着恶念），也不再按着我才行的灭各种的活物了。 22 地还存留的时候，稼穑、寒暑、冬夏、昼夜就永不停息了。”\\

问题：
\begin{itemize}
\item 出方舟后，挪亚做了哪两件事情？
\end{itemize}

\subsubsection{神给人的命令，祝福和立的约 9:1-17}
神赐福给挪亚和他的儿子，对他们说：“你们要生养众多，遍满了地。 2 凡地上的走兽和空中的飞鸟，都必惊恐，惧怕你们，连地上一切的昆虫并海里一切的鱼，都交付你们的手。 3 凡活着的动物，都可以做你们的食物，这一切我都赐给你们，如同菜蔬一样。 4 唯独肉带着血，那就是它的生命，你们不可吃。 5 流你们血，害你们命的，无论是兽是人，我必讨他的罪，就是向各人的弟兄也是如此。 6 凡流人血的，他的血也必被人所流，因为神造人是照自己的形象造的。 7 你们要生养众多，在地上昌盛繁茂。”

8 神晓谕挪亚和他的儿子说： 9 “我与你们和你们的后裔立约， 10 并与你们这里的一切活物，就是飞鸟、牲畜、走兽，凡从方舟里出来的活物立约。 11 我与你们立约：凡有血肉的，不再被洪水灭绝，也不再有洪水毁坏地了。” 神说：“我与你们并你们这里的各样活物所立的永约，是有记号的。 13 我把虹放在云彩中，这就可做我与地立约的记号了。 14 我使云彩盖地的时候，必有虹现在云彩中， 15 我便记念我与你们和各样有血肉的活物所立的约，水就再不泛滥，毁坏一切有血肉的物了。 16 虹必现在云彩中，我看见，就要记念我与地上各样有血肉的活物所立的永约。” 17 神对挪亚说：“这就是我与地上一切有血肉之物立约的记号了。”\\

问题：
\begin{itemize}
\item 用彩笔画出神赐给挪亚和他的儿子的祝福（红色），命令（绿色）和约（黄色）？
\item 神立约的记号是什么？
\item 神立约的内容是什么？
\item 思考：神为什么选择用立约的方式和人说话？
\end{itemize}



\newpage
\section{English Bible Verses - Noah's Ark and the Great Flood}


\subsection{The reason(s) of the Great Flood 6:5-22}

The Lord saw that the human beings on the earth were very wicked. He also saw that their thoughts were only about evil all the time. The Lord was sorry he had made human beings on the earth. His heart was filled with pain. So the Lord said, “I will destroy all human beings that I made on the earth. And I will destroy every animal and everything that crawls on the earth. I will also destroy the birds of the air. This is because I am sorry that I have made them.” 

But Noah pleased the Lord. This is the family history of Noah. Noah was a good man. He was the most innocent man of his time. He walked with God. Noah had three sons: Shem, Ham and Japheth.

People on earth did what God said was evil. Violence was everywhere. And God saw this evil. All people on the earth did only evil. So God said to Noah, “People have made the earth full of violence. So I will destroy all people from the earth. Build a boat of cypress wood for yourself. Make rooms in it and cover it inside and outside with tar. This is how big I want you to build the boat: 450 feet long, 75 feet wide and 45 feet high. Make an opening around the top of the boat. Make it 18 inches high from the edge of the roof down. Put a door in the side of the boat. Make an upper, middle and lower deck in it. 

I will bring a flood of water on the earth. I will destroy all living things that live under the sky. This includes everything that has the breath of life. Everything on the earth will die. But I will make an agreement with you. You, your sons, your wife and your sons’ wives will all go into the boat. Also, you must bring into the boat two of every living thing, male and female. Keep them alive with you. There will be two of every kind of bird, animal and crawling thing. They will come to you to be kept alive. Also gather some of every kind of food. Store it on the boat as food for you and the animals.” Noah did everything that God commanded him.


\begin{itemize}
\item Why God decided to destroy the world by flood?
\item Why God revealed his plan to Noah? 
%\item God likes to reveal his plan to which kind of people?
\end{itemize}





\subsection{The Duration of the Flood 7:6-16/7:23-24/8:4-19}
\subsubsection{The Flood Begins 7:6-16}
Noah was 600 years old when the flood came. He and his wife and his sons and their wives went into the boat. They went in to escape the waters of the flood. The clean animals, the unclean animals, the birds and everything that crawls on the ground came to Noah. They went into the boat in groups of two, male and female. This was just as God had commanded Noah. 10Seven days later the flood started.
Noah was now 600 years old. The flood started on the seventeenth day of the second month of that year. That day the underground springs split open. And the clouds in the sky poured out rain. The rain fell on the earth for 40 days and 40 nights.

On that same day Noah and his wife, his sons Shem, Ham and Japheth and their wives went into the boat. They had every kind of wild animal and tame animal. There was every kind of animal that crawls on the earth. Every kind of bird was there. They all came to Noah in the boat in groups of two. There was every creature that had the breath of life. One male and one female of every living thing came. It was just as God had commanded Noah. Then the Lord closed the door behind them.

\begin{itemize}
\item God told Noah the flooding how many days before it was coming?
\item How did Noah make all the creatures into the boat?
\item What were the inhabitants in the boat? 
\end{itemize}

\subsubsection{The Flood Ends 7:23-24/8:4-19}
So God destroyed from the earth every living thing that was on the land. This was every man, animal, crawling thing and bird of the sky. All that was left was Noah and what was with him in the boat. And the waters continued to cover the earth for 150 days. After 150 days the water had gone down so much that the boat touched land again. It came to rest on one of the mountains of Ararat. This was on the seventeenth day of the seventh month. The water continued to go down. By the first day of the tenth month the tops of the mountains could be seen.

\begin{itemize}
\item The boat parked on which mountain?
\end{itemize}

Forty days later Noah opened the window he had made in the boat. He sent out a raven. It flew here and there until the water had dried up from the earth. Then Noah sent out a dove. This was to find out if the water had dried up from the ground. The dove could not find a place to land because water still covered the earth. So it came back to the boat. Noah reached out his hand and took the bird. And he brought it back into the boat. After seven days Noah again sent out the dove from the boat. And that evening it came back to him with a fresh olive leaf in its mouth. Then Noah knew that the ground was almost dry. Seven days later he sent the dove out again. But this time it did not come back.

Noah was now 601 years old. It was the first day of the first month of that year. The water was dried up from the land. Noah removed the covering of the boat and saw that the land was dry. By the twenty-seventh day of the second month the land was completely dry. Then God said to Noah, “You and your wife, your sons and their wives should go out of the boat. Bring every animal out of the boat with you—the birds, animals and everything that crawls on the earth. Let them have many young ones and let them grow in number.” So Noah went out with his sons, his wife and his sons’ wives. Every animal, everything that crawls on the earth and every bird went out of the boat. They left by families.

\begin{itemize}
\item Which is correct?\\
A. Noah removed the covering of the boat and saw that the land was dry, so he and his family walked out of the boat.\\
B. God said to Noah, “You and your wife, your sons and their wives should go out of the boat.” So Noah went out with his family.
\end{itemize}

\subsection{After the Flood}
\subsubsection{Noah's worship 8:20-22}

Then Noah built an altar to the Lord. Noah took some of all the clean birds and animals. And he burned them on the altar as offerings to God. The Lord was pleased with these sacrifices. He said to himself, “I will never again curse the ground because of human beings. Their thoughts are evil even when they are young. But I will never again destroy every living thing on the earth as I did this time. “As long as the earth continues, there will be planting and harvest. Cold and hot, summer and winter, day and night will not stop.”

\begin{itemize}
\item What did Noah do after he went out of the boad?
\end{itemize}



\subsubsection{The agreement, blessings and command from God}

Then God blessed Noah and his sons. He said to them, “Have many children. Grow in number and fill the earth. Every animal on earth and every bird in the sky will respect and fear you. So will every animal that crawls on the ground and every fish in the sea respect and fear you. I have given them to you. “Everything that moves, everything that is alive, is yours for food. Earlier I gave you the green plants. And now I give you everything for food. But you must not eat meat that still has blood in it, because blood gives life. I will demand your blood for your lives. That is, I will demand the life of any animal that kills a person. And I will demand the life of anyone who takes another person’s life. “Whoever kills a human being, will be killed by a human being. This is because God made humans in his own image. Noah, I want you and your family to have many children. Grow in number on the earth and become many.”


Then God said to Noah and his sons, “Now I am making my agreement with you and your people who will live after you. And I also make it with every living thing that is with you. It is with the birds, the tame animals and the wild animals. It is with all that came out of the boat with you. I make my agreement with every living thing on earth. I make this agreement with you: I will never again destroy all living things by floodwaters. A flood will never again destroy the earth.”

And God said, “I am making an agreement between me and you and every living creature that is with you. It will continue from now on. This is the sign: I am putting my rainbow in the clouds. It is the sign of the agreement between me and the earth. When I bring clouds over the earth, a rainbow appears in the clouds. Then I will remember my agreement. It is between me and you and every living thing. Floodwaters will never again destroy all life on the earth. When the rainbow appears in the clouds, I will see it. Then I will remember the agreement that continues forever. It is between me and every living thing on the earth.” So God said to Noah, “That rainbow is a sign. It is the sign of the agreement that I made with all living things on earth.”

\begin{itemize}
\item Mark out the blessing (red)/command (green)/agreement (yellow) from God using different color?
\item What is the sign of the agreement from God?
\item Why God made agreement with human beings?
\end{itemize}



\begin{table}[h!]
  \begin{center}
    \caption{How long was Noah in the Ark?}
    \label{tab:table1}
\begin{tabular}{p{.5cm}|p{5.95cm}|p{10.5cm}}\hline\hline
   % \begin{tabular}{l|l|l} % <-- Alignments: 1st column left, 2nd middle and 3rd right, with vertical lines in between
      \textbf{Day} & \textbf{Event	} & \textbf{Bible Reference}\\\hline
  %    $\alpha$ & $\beta$ & $\gamma$ \\      \hline
      0 & Noah, his family and the animals enter the ark&Genesis 7:4 “Seven days from now I will send rain on the earth…\\\hline
      \multirow{2}{.5cm}{7} &\multirow{2}{5.95cm}{Rain Starts–The rain comes down and the fountains of the deep burst forth.}&Genesis 7:4…It will rain for 40 days and 40 nights.\\\cline{3-3}
&&Genesis 7:11 It was the 17th day of the second month of the year.\\\hline
      47 &Rain Ends – The ark floats around looking for a place to land.&Genesis 7:24 The waters flooded the earth for 150 days.(This includes the 40 days of rain)\\\hline
157 &Ark runs a ground on the mountains of Ararat.&Genesis 8:4-5 On the 17th day of the seventh month, the ark came to rest on the mountains of Ararat.\\\hline
231 &Tops of other mountains visible&Genesis 8:5 …The waters continued to go down until the tenth month. On the first day of the month, the tops of the mountains could be seen.\\\hline
 \multirow{4}{.5cm}{271}& \multirow{4}{5.95cm}{Bird reconnaissance. – Noah sent out a raven after 40 more days. – Noah sent out a dove 3 times at 7 day intervals.}&Genesis 8:6-7 After 40 days Noah opened the window he had made in the ark.  He sent a raven out.\\\cline{3-3}
&&Genesis 8:8 Then Noah sent a dove out.\\\cline{3-3}
&&Genesis 8:10 He waited seven more days.\\\cline{3-3}
&&Genesis 8:12 He waited seven more days.\\\hline
351&Noah removed the covering from the ark. &Genesis 8:13 It was the first day of the first month of Noah’s 601st year. The water had dried up from the earth. Then Noah removed the covering from the ark. He saw that the surface of the ground was dry.\\\hline
377&God tells Noah to come out of the ark&Genesis 8:14 By the 27th day of the second month the earth was completely dry.\\\hline
    \end{tabular}
  \end{center}
\end{table}

\newpage
\subsubsection{questions 6:5-22}
\begin{itemize}
\item Why God decided to destroy the world by flood (6:5-7)?
\item Why God revealed his plan to Noah (6:8-22)?
%\item What did you learn about God from these paragraph?\\
%He hates evil people, and he has mercy on people who obey Him.
\end{itemize}

\subsubsection{questions 7:6-16}
\begin{itemize}
\item God told Noah the flooding how many days before it was coming?
\item What were the inhabitants in the boat? 
\item How did Noah make all the animals, birds and all creatures  entered into the boat in such a short time?
\end{itemize}

\subsubsection{questions 8:4-20}
\begin{itemize}
\item The boat parked on which mountain?
\item How long did Noah's family stayed in the boat (7:11/8:14)?
\item What do you think they would do while staying in the boat?
\item Which of the following description is correct?\\
A. When the dove returned to Noah with a fresh olive leaf in its beak, Noah walked out with his family\\
B. Noah sent out the dove, and it did not return, so Noah walked out with his family\\
C. Noah removed the covering of the boat and saw that the land was dry, so hewalked out of the boat.\\
D. God said to Noah, “You and your wife, your sons and their wives should go out of the boat.” So Noah went out with his family.
\end{itemize}

\subsubsection{questions 9:1-6}
\begin{itemize}
\item Which of the following is correct?\\
A. God forbidden human eat meat that has its lifeblood still in it.\\
B. God forbidden human eat meat.
\item Which commands were given to Noah only? \\
A. Be fruitful and increase in number and fill the earth.\\
B. Everything that lives and moves about will be food for you. Just as I gave you the green plants, I now give you everything.\\
C. Whoever sheds human blood, by humans shall their blood be shed.
\end{itemize}

\subsubsection{questions 9:7-17}
\begin{itemize}
\item What is the sign of the covenant?
\item God made  the covenant with :\\
A. Noah\\
B. Noah's descendants after him\\
C. every living creature that came out of the boat\\
\item When the sign of the covenant appears in the clouds, it means\\
A. We will remember God's covenant\\
B. God will remember the covenant\\
C. God will never again destroy all life by the waters of flood.
\end{itemize}

\subsubsection{discussion}
\begin{itemize}
\item What did you lean about the characters of God from today's reading?
\end{itemize}
