

\chapter{创造2 }

\section{questions review of Chapter 1}
\begin{enumerate}[nosep]
\large
\item After which creation, there was the concept of TIME, or the term of DAY appeared? 
\itme Earth was created before the creation of TIME or after?
\item If somebody claimed that: "he or she can give an estimation of the earth". This is "true" or "false"?
\item In God's creation, "space" & "time", which came first?
\item In the 1st day, morning and evening, which appeared first?
\item What was created in the 2nd day?
\item What appeared in the 3rd day?
\item What did God created in the 4th day?
\item What did God created in the 5th day?
\item What did God created in the 6th day?
\item Human beings were created according to whose image?
\item Select which is human being’s food and which is animals food?
\begin{enumerate}[nosep]
\item A, All the trees whose fruits have seeds in them. 
\item B, All the green plants
\end{enumerate}
\end{enumerate}

\section{questions of Chapter 2}

\begin{itemize}
\item (vers 1-3) What did God do on the 7th day? 
\item (vers 1-3) Why did God make 7th day a holy day?
\item (vers 4-7) In the beginning of the creation, how did God watered all the ground?

A, rain \hspace{2cm} B, mist


\item (vers 4-7) What is the material of the man made from?
\item (vers 4-7) The Lord breathed the breath of life into the man’s $_____$ .
\item (vers 8-9) The garden of the Lord God in the east is called $______$.
\item (vers 8-9) What are the names of the 2 trees purticular mentioned in the Lord God's garden? 
\item (vers 8-9) Where they are located in the garden?
\item (vers 10-17) Match the following according to the Bible verse

1st stream  \hspace{2cm}                           A,Euphrates      

2nd stream  \hspace{2cm}  													 B,	Tigris

3rd stream  \hspace{2cm}  														 C,Pishon

4th steam  \hspace{2cm}  														 D,Gihon

\item (vers 10-17) What is the job of the man?
\item (vers 10-17) The Lord God gave command to:

A, man \hspace{2cm}  B, woman  \hspace{2cm}   C, man & woman
\item (vers 10-17) Which tree's fruit can not be eaten?

\item (vers 10-17) According to the command of the Lord God, which tree's fruit can be eaten?
\begin{itemize}
\item 1, The tree that gives life
\item 2, Any tree on the earth the tree which gives the knowledge of good and evil
\item 3, Any tree in the garden except of the the tree which gives the knowledge of good and evil
\end{itemize}
\end{itmeize}






