\chapter{大卫之约 (David/Leo)}

\section{撒母耳上15:17-23 扫罗悖逆，被神废弃为王}
\begin{enumerate}[nosep]
\large
\item What is the nationality of Saul?
\item What is the position (career) of Saul in Israel? 
\item Who anointed Saul as a King over Israel?
\item Do you know how many Israel tribes (bonus question Matthew (19:28)/Luke (22:30))?
\item What was the mission God commanded Saul to do?
\item What type of people the Amalekites were in the eyes of God?
\begin{enumerate}[nosep]
\item The Amalekites prey on the weak when Israel exodus from Egypt.(Exodus 17:8)
\item Remember what the Amalekites did to you along your way from Egypt, how they met you on your journey when you were tired and weary, and they attacked all your stragglers (Deuteronomy 25:17-18)
\item  they had no fear of God (Deuteronomy 25:17-18)
\end{enumerate}
\item What were the uncomplete part of mission that Saul did not finish?
\begin{enumerate}[nosep]
\item Saul brought back Agag their king
\item The soldiers took best of sheep and cattle from the plunder
\end{enumerate}
\item The soldiers took sheep and cattle from the plunder, who should be blamed?
\item What delights the LORD:\\
 A, burnt offerings and sacrifices;\hspace{2cm} B, obeying the Lord
\item What was the punishment of Saul after he had rejected the word of the Lord?
\end{enumerate}

\section{撒母耳上16:1 神差撒母耳去伯利恒}
\begin{enumerate}[nosep]
\large
\item Where did the LORD send Samuel to go?
\item Whose son did the LORD ask Samuel to visit?
\item What was the mission about Samuel's trip?
\item Do you know which city Jesus was born (bonus question)?
\end{enumerate}

\section{撒母耳上16:10-13 撒母耳膏大卫}
\begin{enumerate}[nosep]
\large
\item How many sons that Jesse had? (8)
\item What was the job of Jesse's youngest son?
\item What was the name of the new king?
\item What was the change after David was anointed in the presence of his brothers?
\item Do you all admire to aquire the Holy Spirit from God?
\end{enumerate}

\section{撒母耳上22:1-2/24:1-2 扫罗到隐基底追杀大卫}
\begin{enumerate}[nosep]
\large
\item How many people were followed David? What type of the people stayed with David? (400)
\item How many did Saul took with him? What type of the people did Saul take with him? 
\end{enumerate}

\section{撒母耳上24:3-15 大卫第一次饶恕扫罗（大便）}
\begin{enumerate}[nosep]
\large
\item Why did Saul come to the sheep pens?
\item 24:3 “I will give your enemy into your hands", your enemy refers to whom?
\item Why did David forbidden his followers attack Saul?
\item Why did Saul take so many people with him to look for David?
\item Did David plea Saul to save his life in his statement?
\item According to the defending words, David asked whom to be the final vindicator and deliver him from his enemy's hand?
\end{enumerate}


\section{撒母耳下 5:1-5 大卫做王的时间}
\begin{table}[H]\centering
\begin{tabular}{p{3.75cm}|p{5.75cm}|p{3.75cm}}\hline\hline
period as the king&the king for which tribe(s) & name of city\\\hline
&&\\\hline
&&\\\hline
\end{tabular}
\end{table}

\section{撒母耳下 7:1-7 大卫起意要建殿}
Nathan said to David, "Whatever you have in mind, go ahead and do it", what was the thought in David's mind?

\section{撒母耳下 7:8-16 神给大卫的应许}

\begin{table}[H]\centering
\begin{tabular}{p{3.75cm}|p{3cm}|p{2.75cm}|p{5.25cm}}\hline\hline
 things the LORD had done for David&the promises to Israelities&the promises gave to David&the promises to David's descendants\\\hline
 &&&\\
  &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
 &&&\\
\end{tabular}
\end{table}









\begin{table}[H]\centering
\begin{tabular}{p{3.75cm}|p{3cm}|p{2.75cm}|p{5.25cm}}\hline\hline
 things the LORD had done for David&the promises to Israelities&the promisesgave to David&the promises to David's descendants\\\hline
(8-9a) &10&9b, 11&12-16\\\hline
appointed you ruler over my people Israel&provide a place for my people Israel&make your name great&The LORD will raise up your offspring to succeed you,establish his kingdom\\\hline
be with you wherever you have gone&plant them so that they can have a home of their own and no longer be disturbed&give you rest from all your enemies&build a house for my Name, and I will establish the throne of his kingdom forever\\\hline
cut off all your enemies from before you&Wicked people will not oppress them anymore&establish a house for you&I will be his father, and he will be my son. When he does wrong, I will punish him with a rod wielded by men, with floggings inflicted by human hands. But my love will never be taken away from him, as I took it away from Saul, whom I removed from before you. \\\hline
\end{tabular}
\end{table}













