\chapter{犯罪 Rachael、Joyce，Leo，Stefanie，David，Selina，Ethan，Adriana}
\iffalse
\section{Bible verses}
1 Now the serpent was more deceitful than any other animal that Jehovah had made; and it said to the woman, "Has God really said, 'You shall not eat from any tree of the garden'?" The woman answered, "We may eat of the fruit of all the trees of the garden except the fruit of the tree which is in the middle of the garden, for God has said, 'You shall not eat from it, nor shall you touch it; for if you do, you shall die.'" Then the serpent said to the woman, "You shall not surely die; for God knows that as soon as you eat of it your eyes will be opened, and you will know what is good and what is evil."


When the woman saw that the tree was good for food, beautiful to look at and that it would make her wise, she took some of its fruit and ate it. Then she gave some to her husband who was with her, and he ate.
Then the eyes of both of them were opened, so that they knew that they were naked; and they sewed fig-leaves together and made girdles for themselves. When they heard the sound of the footsteps of Jehovah, as he was walking in the garden in the cool of the day, the man and his wife hid from him among the trees of the garden.

And Jehovah called to the man and said to him, "Where are you?" and he answered, "I heard the sound of thy footsteps in the garden and I was afraid, because I was naked; so I hid myself." Jehovah said, "Who told you that you were naked? Have you eaten from the tree from which I forbade you to eat?" The man answered, "The woman whom thou didst give to me—she gave me fruit from the tree and I ate." Jehovah said to the woman, "What is this that you have done?" The woman replied, "The serpent deceived me, and I ate."

Then Jehovah said to the serpent, "Because you have done this, you shall be hated more than all beasts. You shall crawl on your belly and eat dust all your life, and men and serpents shall always be enemies. They shall bruise your head, and you shall wound them on the heel."

To the woman he said, "I will greatly increase your trouble and your pain, and you shall be subject to your husband, and he shall rule over you."

But to the man he said, "Because you have listened to your wife and have eaten of the tree from which I forbade you to eat, as long as you live you shall earn a living only by hard work. By hard work shall you raise food to eat. And you shall die and your body go back to the ground, for from dust you were made, and to dust you shall return!"

And Jehovah made garments of skins for the man and his wife, and clothed them. And he sent them out of the garden of Eden to till the ground.
\fi






\section{Bible verses}
\subsection{verse 1-6}
\large{
1 Now the snake was the most clever of all the wild animals the Lord God had made. One day the snake spoke to the woman. He said, “Did God really say that you must not eat fruit from any tree in the garden?” 2 The woman answered the snake, “We may eat fruit from the trees in the garden. 3 But God told us, ‘You must not eat fruit from the tree that is in the middle of the garden. You must not even touch it, or you will die.’” 4 But the snake said to the woman, “You will not die. 5 God knows that if you eat the fruit from that tree, you will learn about good and evil. Then you will be like God!” 6 The woman saw that the tree was beautiful. She saw that its fruit was good to eat and that it would make her wise. So she took some of its fruit and ate it. She also gave some of the fruit to her husband who was with her, and he ate it.}
\begin{itemize}
\item Q1: After spoken with the snake, what did the woman saw, and what caused her eat the fruit from the tree which gives the knowledge of good and evil?
\item Q2: Who was the first one eat the fruit?
\end{itemize}

\subsection{verse 7-13}
\large{7 Then, it was as if the man’s and the woman’s eyes were opened. They realized they were naked. So they sewed fig leaves together and made something to cover themselves. 8 Then they heard the Lord God walking in the garden. This was during the cool part of the day. And the man and his wife hid from the Lord God among the trees in the garden. 9 But the Lord God called to the man. The Lord said, “Where are you?” 10 The man answered, “I heard you walking in the garden. I was afraid because I was naked. So I hid.” 11 God said to the man, “Who told you that you were naked? Did you eat fruit from that tree? I commanded you not to eat from that tree.” 12 The man said, “You gave this woman to me. She gave me fruit from the tree. So I ate it.”
13 Then the Lord God said to the woman, “What have you done?” She answered, “The snake tricked me. So I ate the fruit.”}

\begin{itemize}
\item Q3: What was the 1st thing the man and the woman realized after ate the fruit (or in another word, what was the 1st knowledge they gain after ate the fruit)?
\item Q4: Then, what they did for themselves?
\item Q5: When they heard the Lord God walking in the garden, where did they stay?
\item Q6: The Lord God spoke to which person first (man or woman)?
\item Q7: What was the first question the Lord God asked to human being?
\item Q8: What was the reason of the man hidden from the Lord God?
\item Q9: When the Lord God asked the man "Did you eat fruit from that tree", what was the correct answer the man should give? 
\end{itemize}


\subsection{verse 14-20}
\large{
14 The Lord God said to the snake, “Because you did this, a curse will be put on you. You will be cursed more than any tame animal or wild animal. You will crawl on your stomach, and you will eat dust all the days of your life. 15 I will make you and the woman enemies to each other. Your descendants and her descendants will be enemies. Her child will crush your head. And you will bite his heel.”
16 Then God said to the woman, “I will cause you to have much trouble when you are pregnant. And when you give birth to children, you will have great pain. You will greatly desire your husband, but he will rule over you.”
17 Then God said to the man, “You listened to what your wife said. And you ate fruit from the tree that I commanded you not to eat from. So I will put a curse on the ground. You will have to work very hard for food. In pain you will eat its food all the days of your life. 18 The ground will produce thorns and weeds for you. And you will eat the plants of the field. 19 You will sweat and work hard for your food. Later you will return to the ground. This is because you were taken from the ground. You are dust. And when you die, you will return to the dust.” 20 The man named his wife Eve\footnote{This name sounds like the Hebrew word meaning “alive.”}.  This is because she is the mother of everyone who ever lived.}

\begin{itemize}
\item Q10: When the Lord God announced the punishment toward the man, the woman and the snake, what was the sequence (or order), i.e., man/woman/snake, woman/man/snake...)
\item Q11: What was the new name the man gave to his wife?
\end{itemize}

\subsection{verse 21-24}
\large{21 The Lord God made clothes from animal skins for the man and his wife. And so the Lord dressed them. 22 Then the Lord God said, “Look, the man has become like one of us. He knows good and evil. And now we must keep him from eating some of the fruit from the tree of life. If he does, he will live forever.” 23 So the Lord God forced the man out of the garden of Eden. He had to work the ground he was taken from. 24 God forced the man out of the garden. Then God put angels on the east side of the garden. He also put a sword of fire there. It flashed around in every direction. This kept people from getting to the tree of life.}

\begin{itemize}
\item Q12: The Lord God made clothese from what kind of material?
\item Q13: What will be the function of the fruit from the tree of life if the man ate it?
\end{itemize}

\newpage
%\section{Student Reading}
1 Now the snake was the most clever of all the wild animals the Lord God had made. One day the snake spoke to the woman. He said, “Did God really say that you must not eat fruit from any tree in the garden?” 2 The woman answered the snake, “We may eat fruit from the trees in the garden. 3 But God told us, ‘You must not eat fruit from the tree that is in the middle of the garden. You must not even touch it, or you will die.’” 4 But the snake said to the woman, “You will not die. 5 God knows that if you eat the fruit from that tree, you will learn about good and evil. Then you will be like God!” 6 The woman saw that the tree was beautiful. She saw that its fruit was good to eat and that it would make her wise. So she took some of its fruit and ate it. She also gave some of the fruit to her husband who was with her, and he ate it.\\
\\
7 Then, it was as if the man’s and the woman’s eyes were opened. They realized they were naked. So they sewed fig leaves together and made something to cover themselves. 8 Then they heard the Lord God walking in the garden. This was during the cool part of the day. And the man and his wife hid from the Lord God among the trees in the garden. 9 But the Lord God called to the man. The Lord said, “Where are you?” 10 The man answered, “I heard you walking in the garden. I was afraid because I was naked. So I hid.” 11 God said to the man, “Who told you that you were naked? Did you eat fruit from that tree? I commanded you not to eat from that tree.” 12 The man said, “You gave this woman to me. She gave me fruit from the tree. So I ate it.”
13 Then the Lord God said to the woman, “What have you done?” She answered, “The snake tricked me. So I ate the fruit.”\\
\\
14 The Lord God said to the snake, “Because you did this, a curse will be put on you. You will be cursed more than any tame animal or wild animal. You will crawl on your stomach, and you will eat dust all the days of your life. 15 I will make you and the woman enemies to each other. Your descendants and her descendants will be enemies. Her child will crush your head. And you will bite his heel.”
16 Then God said to the woman, “I will cause you to have much trouble when you are pregnant. And when you give birth to children, you will have great pain. You will greatly desire your husband, but he will rule over you.”
17 Then God said to the man, “You listened to what your wife said. And you ate fruit from the tree that I commanded you not to eat from. So I will put a curse on the ground. You will have to work very hard for food. In pain you will eat its food all the days of your life. 18 The ground will produce thorns and weeds for you. And you will eat the plants of the field. 19 You will sweat and work hard for your food. Later you will return to the ground. This is because you were taken from the ground. You are dust. And when you die, you will return to the dust.” 20 The man named his wife Eve\footnote{This name sounds like the Hebrew word meaning “alive.”}.  This is because she is the mother of everyone who ever lived.\\
21 The Lord God made clothes from animal skins for the man and his wife. And so the Lord dressed them. 22 Then the Lord God said, “Look, the man has become like one of us. He knows good and evil. And now we must keep him from eating some of the fruit from the tree of life. If he does, he will live forever.” 23 So the Lord God forced the man out of the garden of Eden. He had to work the ground he was taken from. 24 God forced the man out of the garden. Then God put angels on the east side of the garden. He also put a sword of fire there. It flashed around in every direction. This kept people from getting to the tree of life.




\newpage
\section{Discussions}
\normalsize
\begin{itemize}
\item Q1: Compare the words between the Lord God and the snake, and find out all the differences between them. Hints:\\
\begin{itemize}
\item 1, find out which information were in God's original command, but missing in the snake's words?
\item 2, which concept (or term used by God) became vague in the snake's question?
\item 3, which information were not in the God's words, but added by the snake?
\item 4, the snake changed which word(s) of God?
\item 5, or any other differences you found


\begin{table}[H]\centering
\begin{tabular}{p{7.75cm}|p{9.75cm}}\hline\hline
%\begin{tabular}{l|l}\hline
神說&蛇說\\\hline
園中各樣樹上的果子，你可以隨意吃； 17 只是分別善惡樹上的果子，你不可吃，因為你吃的日子必定死。
&神豈是真說，不許你們吃園中所有樹上的果子嗎？
\\\cline{2-2}
&你們不一定死！ 5 因為神知道你們吃的日子眼睛就明亮了，你們便如神能知道善惡。
\\\hline
\end{tabular}
\end{table}
\begin{table}[H]
\arrayrulecolor{black}
\centering 
\begin{tabular}{p{9.cm}|p{8.5cm}}\hline\hline
神說&女人說\\\hline
園中各樣樹上的果子，你可以隨意吃； 17 只是分別善惡樹上的果子，你不可吃，因為你吃的日子必定死。
&園中樹上的果子我們可以吃， 3 唯有園當中那棵樹上的果子，神曾說：『你們不可吃，也不可摸，免得你們死。』\\\hline
\end{tabular}
\end{table}



\begin{table}[H]\centering
\begin{tabular}{p{7.75cm}|p{9.75cm}}\hline\hline
%\begin{tabular}{l|l}\hline
The Lord God' command&The snake's question\\\hline
\multirow{2}{7.9cm}{\textbf{You may eat the fruit from any tree in the garden. But you must not eat the fruit from the tree which gives the knowledge of good and evil. If you ever eat fruit from that tree, you will die!}}
&\textbf{Did God really say that you must not eat fruit from any tree in the garden}?
\\\cline{2-2}
&\textbf{You will not die. God knows that if you eat the fruit from that tree, you will learn about good and evil. Then you will be like God!}
\\\hline
\end{tabular}
\end{table}
\begin{itemize}
\item write down all the differences here
\item
\item summerize all the tricks that the snake had used to lead the woman walk out of the command of God.
\end{itemize}
\end{itemize}
\begin{tikzpicture}
\draw[very thick](-1,0) circle (1.);
\draw (-1.5,-2.75) node[below=3pt] {} node[above=3pt] {the original circle};
\draw[very thick,- ] (4.5,0) arc (2.5:340:1.);
\draw (3.,-2.750) node[below=3pt] {} node[above=3pt] {wipe out partial};
\draw (3.,-3.25) node[below=3pt] {} node[above=3pt] {of the circle};
\draw (3.,-3.75) node[below=3pt] {} node[above=3pt] {(trick 1)};
\draw (6,-3.75) node[below=3pt] {} node[above=3pt] {(trick 2)};
\draw (9.5,-3.75) node[below=3pt] {} node[above=3pt] {(trick 3)};
\draw (12.5,-3.75) node[below=3pt] {} node[above=3pt] {(trick 4)};
\end{tikzpicture}


\item Q2: Compare the words between the Lord God and the woman, and find out all the differences. Hints:
\begin{itemize}
\item 1, which information, the woman had deleted from God's original command?
\item 2, what were the extra words that the woman added?
\item 3, or any other differences you found
\end{itemize}
\begin{table}[H]
\arrayrulecolor{black}
\centering 
\begin{tabular}{p{9.cm}|p{8.5cm}}\hline\hline
The Lord God' command&The woman's answer\\\hline
\textbf{You may eat the fruit from any tree in the garden. But you must not eat the fruit from the tree which gives the knowledge of good and evil. If you ever eat fruit from that tree, you will die!}
%&\textbf{Did God really say that you must not eat fruit from any tree in the garden}?
&\textbf{We may eat fruit from the trees in the garden. But God told us, ‘You must not eat fruit from the tree that is in the middle of the garden. You must not even touch it, or you will die.}’\\\hline
\end{tabular}
\end{table}

\item What are the consequences of eating 2 trees the Lord God set in the middle of garden? Which tree was revealed to them first? Why the Lord God set the tree which gives good and evil?
\item When they ate the fruit from tree which gives good and evil, didn't God know? Why God did not stop them?
\item And the man put the responsibility of eating fruit on to whom?
\item The woman put her responsibility of eating fruit on to whom?
\item The man and his wife were naked, but they were not ashamed. Why  (Gen 2:25).

\end{itemize}














