\documentclass{letter}
\signature{\bfseries{\textbf{Kaixin, Wang}}}
\address{The Graduate College\\ 
The University of Texas Rio Grande Valley\\ 
Marialice Shary Shivers Bldg. 1.158\\
1201 W. University Drive\\
Edinburg, TX 78539-2999\\}


%CIPD Level 7 Diploma in Human Resource Management
\begin{document}




\begin{letter}{Dear Admissions Committee,}
\opening{}
%\dots


I am writing this letter of intent to express my strong desire to pursue a Master of Computer Science at UTRGV. With my educational background in MA and BA, and valuable working experiences in various roles such as Sales Assistant, Business Assistant, Brand Ambassador, and HR, I have realized the critical importance of technology and its advancements in the modern workplace. In these positions, I have observed the pivotal role that computer science plays in enhancing productivity, efficiency, and communication.



There are several reasons why I am keen to deepen my knowledge and skills in computer science. Firstly, I have recognized the importance of efficiently querying the most useful information, which greatly influences sales decisions and relative strategies. With the increasing amount of information available today, I need to improve my search techniques with professional help through further learning of the most advanced technology. Moreover, I want to learn how to handle and manage large amounts of data and use various advanced techniques, analysis, and intuitive visualization to improve decision-making processes.





Secondly, I have identified that the BIBLIO software used in my current company has more room for improvement. For example, it requires redundant manual data input during the final contract generating stage even though the data already exists in the database. These kinds of extra human interactions can greatly lower efficiency and inevitably increase the risks of human typos. Thus, I am so eagerly motivated to develop more sophisticated and highly automated software for sales companies by designing a more user-friendly UI, equipped with a more secure and efficient sales data management technique.


%Furthermore, I have observed a security issue while generating the final order in my current position. When I input the purchase order, the system opens a new window for each part of the order, and when I log off the purchase order, I have to manually close all the windows. If any window is left to close, I found that I am still able to access this purchase order through an unclosed window even after I have logged out of the system.




Moreover, I found that the database used in my current company between the sales and shipping departments are not well connected or matched. Sometimes, the product amount was 3 pieces in the purchase order, however, the shipping department sent 3 boxes which resulted in 6 pieces/box $X$ 3 boxes = 18 pieces being shipped from the UK to our China office. Or sometimes, the shipping department sent multiple deliveries for the same purchase order! There are so many extra copies of wrong delivered attractively packaged books piled in our office, which becomes a heavy burden and a headache for our office manager. These kinds of mistakes tremendously reduced the profits for the company.


My future goal and dream after education is to run my own software company using the professional and advanced techniques from computer science and previous education, combined with my working experiences.  With the knowledge of Artificial Intelligence, Machine Learning and cloud-based database management system, I hope to provide various consultancy services to sales companies  to help them implement more advanced sales strategies; a more safe and efficient designed database management system; a more user-friendly and user-centered UI with human-computer interaction.



After researching various institutions, I am impressed by UTRGV's rankings and recognitions, the Master of Computer Science program's accreditation and cutting-edge curriculum, as well as the experienced and dedicated faculty who teach it, further inspire my interest. Moreover, UTRGV's affordability and its practical course are other major factors that draw me to the university. %Finally, UTRGV's demonstrated commitment to student success is inspiring. The university has a track record of helping students succeed in research, professional certification, and career advancement. 



Overall, I am excited about the prospect of being a part of this vibrant academic community and contributing to its ongoing success. I am confident that UTRGV's Master of Computer Science program is the ideal choice for me to achieve my academic and career goals. I look forward to the opportunity to learn from and work alongside the faculty and classmates and to contribute to the program's continued success. 

Thank you for considering my application.














%\closing{Sincerely,}






\closing{Yours Faithfully,}
%\ps{P.S. Here goes your ps.}
%\encl{Kai Xin, Wang}

%Kai Xin, Wang
\end{letter}
\end{document}




%\begin{letter}{%Director \\ Doe \& Co \\ 35 Anthony Road
%\\ Newport \\ Ipswich IP3 5RT}
%\opening{Dear Sir or Madam:}



%\ps

%P.S. You can find the full text of GFDL license at
%\url{http://www.gnu.org/copyleft/fdl.html}.

%\encl{Copyright permission form}

%\end{letter}
%\end{document}