\chapter{The born of Jesus 耶稣出生 (Leo/Luna/Selina/Lumi(xixi)}

\section{老师版本Verse and Questions}
\subsection{Fullfilled the promise to the seed of Abraham应验亚伯拉罕应许}

\subsubsection{English Bible Verse (Mathew1:1/Genesis 22:16-18/Galatians 3:16)}
\textbf{Mathew1:1} This is the genealogy of Jesus the Messiah the son of David, the son of Abraham:\\
\textbf{Genesis 22:16-18} “By Myself I have sworn”, says the Lord, “because you have done this thing, and have not withheld your son, your only son— 17 blessing I will bless you, and multiplying I will multiply your descendants as the stars of the heaven and as the sand which is on the seashore; and your descendants shall possess the gate of their enemies. 18 In your seed all the nations of the earth shall be blessed, because you have obeyed My voice.”\\
\textbf{Galatians 3:16} The promises were spoken to Abraham and to his seed. Scripture does not say “and to seeds,” meaning many people, but “and to your seed,”  meaning one person, who is Christ.

\subsubsection{questions}
\textbf{1 Whose Son Is Jesus?}\\
\textbf{2 In the statement of "I swear by myself", "I" refers to whom?}\\
\textbf{3 "you have done this", "you" refers to whom?}\\
\textbf{4 "you have done this and have not withheld your son", what does this mean? What did Abraham do with his son?}\\
\textbf{5 Why did Abraham sacrify his only son?}\\
\textbf{6 When Abraham sacrified his only son, God promised to bless Abraham with how many descendants?}\\
\textbf{7 God promised Abraham to bless all nations through whom?}\\
\textbf{8 According to God's promise to Abraham, how all the nations of the earth shall be blessed?}\\
\textbf{9 Who is the seed to bless all the nations on earth？}\\


\subsection{Fullfilled the promise to the seed of David 应验大卫后裔应许}

%賽61:1 主耶和華的靈在我身上，因為耶和華用膏膏我，叫我傳好信息給謙卑的人，差遣我醫好傷心的人，報告被擄的得釋放、被囚的出監牢\\
%伯2:14-15 兒女既同有血肉之體，他也照樣親自成了血肉之體，特要藉著死敗壞那掌死權的，就是魔鬼， 15 並要釋放那些一生因怕死而為奴僕的人。

\subsubsection{The promises to the seed of David (Mathew1:1/2Samuel 7:8-14)}
\textbf{Mathew1:1} This is the genealogy of Jesus the Messiah the son of David, the son of Abraham:\\
\textbf{2Samuel 7:8-14} Now therefore, thus shall you say to My servant David, ‘Thus says the Lord of hosts: “ ...I will set up your seed after you, who will come from your body, and I will establish his kingdom. 13 He shall build a house for My name, and I will establish the throne of his kingdom forever. 14 I will be his Father, and he shall be My son. .....\\

%\subsubsection{questions Mathew 1:1/2Samuel 7:8-14}
\textbf{1 What are the promises God give to David's seed?}\\


%\subsection{Set up the kingdom of David's seed foreever }
\subsubsection{Set up the kingdom of David's seed foreever (Luke 2:8-11/Mathew 2:1-6)}
\textbf{Luke 2:8-11} 8 Nearby shepherds were living in the fields, guarding their sheep at night. 9 The Lord’s angel stood before them, the Lord’s glory shone around them, and they were terrified. 10 The angel said, “Don’t be afraid! Look! I bring good news to you—wonderful, joyous news for all people. 11 Your savior is born today in David’s city. He is Christ the Lord.”\\
\textbf{Mathew 2:1-6} 1 Now after Jesus was born in Bethlehem of Judea in the days of Herod the king, behold, wise men from the East came to Jerusalem, 2 saying, “Where is He who has been born King of the Jews? For we have seen His star in the East and have come to worship Him.”
3 When Herod the king heard this, he was troubled, and all Jerusalem with him. 4 And when he had gathered all the chief priests and scribes of the people together, he inquired of them where the Christ was to be born.
5 So they said to him, “In Bethlehem of Judea, for thus it is written by the prophet:
6 ‘But you, Bethlehem, in the land of Judah,
Are not the least among the rulers of Judah;
For out of you shall come a Ruler
Who will shepherd My people Israel.’ ”\\

\textbf{1 The good news is for which type of people?}\\
A. Jewish \hspace{1cm} B. Chinese \hspace{1cm} C. All the nations\\
\textbf{2 The baby was born in which city?}\\
\textbf{3 What is the identity of the new born baby?}\\

\subsubsection{Build a house for God's name (John 2:19-22)}
19 Jesus answered and said to them, “Destroy this temple, and in three days I will raise it up.”
20 Then the Jews said, “It has taken forty-six years to build this temple, and will You raise it up in three days?”
21 But He was speaking of the temple of His body. 22 Therefore, when He had risen from the dead, His disciples remembered that He had said this to them; and they believed the Scripture and the word which Jesus had said.\\

\textbf{1 When will the new temple be built?}\\
\textbf{2 What is the new temple built by?}\\


\iffalse
\subsubsection{English Bible Verse (Isaiah 61:1/Hebrews 2:14-15)}
\textbf{Isaiah 61:1} The Spirit of the Lord God is on Me, because the Lord has anointed Me to bring good news to the poor. He has sent Me to heal the brokenhearted, to proclaim liberty to the captives, and freedom to the prisoners\\
\textbf{Hebrews 2:14-15} Therefore, since the children share in flesh and blood, Jesus also shared the same things in the same way. He did this to destroy the one who holds the power over death—the devil—by dying. 15 He set free those who were held in slavery their entire lives by their fear of death.\\

\subsubsection{questions Isaiah 61:1/Hebrews 2:14-15}
\textbf{1 "me" refers to whom?}\\
\textbf{2 What are the tasks of the new born baby?}\\
\textbf{3 Does anybody know the meaning of Christ/Messiah?}\\
\textbf{4 "children share in flesh and blood", children refer to whom?}\\
\textbf{5 Who holds the power over death?}\\
\textbf{6 Who destroyd devil's power over death?}\\
\fi


\subsection{The promises to the seed of woman (应验女人后裔、耶稣名字的意义)}


\subsubsection{English Bible Verse （Matthew 1:18-23/Isaiah 7:14/Genesis 3:15）}
\textbf{Matthew 1:18-23} This is how the birth of Jesus Christ took place. When Mary his mother was engaged to Joseph, before they were married, she became pregnant by the Holy Spirit. 19 Joseph her husband was a righteous man. Because he didn’t want to humiliate her, he decided to call off their engagement quietly. 20 As he was thinking about this, an angel from the Lord appeared to him in a dream and said, “Joseph son of David, don’t be afraid to take Mary as your wife, because the child she carries was conceived by the Holy Spirit. 21 She will give birth to a son, and you will call him Jesus, because he will save his people from their sins.” 22 Now all of this took place so that what the Lord had spoken through the prophet would be fulfilled:
23 Look! A virgin will become pregnant and give birth to a son, And they will call him, Emmanuel.\\
\textbf{Isaiah 7:14} Therefore the Lord himself will give you a sign: behold, a virgin shall conceive, and bear a son, and shall call his name Immanuel.\\
\textbf{Genesis 3:15} And I will put enmity between you and the woman, and between your seed and her Seed; He shall bruise your head, and you shall bruise His heel.\\


\subsection{question （Matthew 1:18-23/Isaiah 7:14/Genesis 3:15）}
\textbf{Which statement is correct?}\\
Jesus has a biological mather only.    \hspace{1cm} Jesus has biological father. \\
\textbf{What is the meaning of Jesus?}\\
\textbf{What is the purpose of Jesus coming to this world?}\\
\textbf{The birth of Jesus performed which promise?}\\


\newpage
\section{学生版本 English Bible Verses}
\subsection{Fullfilled promise to seed of Abraham (Mathew1:1/Genesis 22:16-18/Galatians 3:16)}
\textbf{Mathew1:1} This is the genealogy of Jesus the Messiah the son of David, the son of Abraham:\\
\textbf{Genesis 22:16-18} “By Myself I have sworn”, says the Lord, “because you have done this thing, and have not withheld your son, your only son— 17 blessing I will bless you, and multiplying I will multiply your descendants as the stars of the heaven and as the sand which is on the seashore; and your descendants shall possess the gate of their enemies. 18 In your seed all the nations of the earth shall be blessed, because you have obeyed My voice.”\\
\textbf{Galatians 3:16} The promises were spoken to Abraham and to his seed. Scripture does not say “and to seeds,” meaning many people, but “and to your seed,”  meaning one person, who is Christ.\\

\subsection{Fullfilled the promise to the seed of David}
\subsubsection{The promises to the seed of David (Mathew1:1/2Samuel 7:8-14)}
\textbf{Mathew1:1} This is the genealogy of Jesus the Messiah the son of David, the son of Abraham:\\
\textbf{2Samuel 7:8-14} Now therefore, thus shall you say to My servant David, ‘Thus says the Lord of hosts: “ ...I will set up your seed after you, who will come from your body, and I will establish his kingdom. 13 He shall build a house for My name, and I will establish the throne of his kingdom forever. 14 I will be his Father, and he shall be My son. 

\subsubsection{Set up the kingdom of David's seed foreever (Luke 2:8-11/Mathew 2:1-6)}
\textbf{Luke 2:8-11} 8 Nearby shepherds were living in the fields, guarding their sheep at night. 9 The Lord’s angel stood before them, the Lord’s glory shone around them, and they were terrified. 10 The angel said, “Don’t be afraid! Look! I bring good news to you—wonderful, joyous news for all people. 11 Your savior is born today in David’s city. He is Christ the Lord.”\\
\textbf{Mathew 2:1-6} 1 Now after Jesus was born in Bethlehem of Judea in the days of Herod the king, behold, wise men from the East came to Jerusalem, 2 saying, “Where is He who has been born King of the Jews? For we have seen His star in the East and have come to worship Him.”
3 When Herod the king heard this, he was troubled, and all Jerusalem with him. 4 And when he had gathered all the chief priests and scribes of the people together, he inquired of them where the Christ was to be born.
5 So they said to him, “In Bethlehem of Judea, for thus it is written by the prophet:
6 ‘But you, Bethlehem, in the land of Judah,
Are not the least among the rulers of Judah;
For out of you shall come a Ruler
Who will shepherd My people Israel.’ ”

\subsubsection{Build a house for God's name (John 2:19-22)}
19 Jesus answered and said to them, “Destroy this temple, and in three days I will raise it up.”
20 Then the Jews said, “It has taken forty-six years to build this temple, and will You raise it up in three days?”
21 But He was speaking of the temple of His body. 22 Therefore, when He had risen from the dead, His disciples remembered that He had said this to them; and they believed the Scripture and the word which Jesus had said.\\

\subsection{Fulfilled promise of woman's seed （Matthew 1:18-23/Isaiah 7:14/Genesis 3:15）}
\textbf{Matthew 1:18-23} This is how the birth of Jesus Christ took place. When Mary his mother was engaged to Joseph, before they were married, she became pregnant by the Holy Spirit. 19 Joseph her husband was a righteous man. Because he didn’t want to humiliate her, he decided to call off their engagement quietly. 20 As he was thinking about this, an angel from the Lord appeared to him in a dream and said, “Joseph son of David, don’t be afraid to take Mary as your wife, because the child she carries was conceived by the Holy Spirit. 21 She will give birth to a son, and you will call him Jesus, because he will save his people from their sins.” 22 Now all of this took place so that what the Lord had spoken through the prophet would be fulfilled:
23 Look! A virgin will become pregnant and give birth to a son, And they will call him, Emmanuel.\\
\textbf{Isaiah 7:14} Therefore the Lord himself will give you a sign: behold, a virgin shall conceive, and bear a son, and shall call his name Immanuel.\\
\textbf{Genesis 3:15} And I will put enmity between you and the woman, and between your seed and her Seed; He shall bruise your head, and you shall bruise His heel.



\section{Birth of Jesus (Luke 2:7-20) 耶稣降生在馬槽，牧羊人探访(路2:7-20)}
\subsection{耶稣的降生(路2:7-20)}
生了頭胎的兒子，用布包起來，放在馬槽裡，因為客店裡沒有地方。8 在伯利恆之野地裡有牧羊的人，夜間按著更次看守羊群。 9 有主的使者站在他們旁邊，主的榮光四面照著他們，牧羊的人就甚懼怕。 10 那天使對他們說：「不要懼怕，我報給你們大喜的信息，是關乎萬民的。 11 因今天在大衛的城裡，為你們生了救主，就是主基督。 12 你們要看見一個嬰孩，包著布，臥在馬槽裡，那就是記號了。」 13 忽然有一大隊天兵，同那天使讚美神說： 14 「在至高之處榮耀歸於神！在地上平安歸於他所喜悅的人！」

15 眾天使離開他們升天去了，牧羊的人彼此說：「我們往伯利恆去，看看所成的事，就是主所指示我們的。」 16 他們急忙去了，就尋見馬利亞和約瑟，又有那嬰孩臥在馬槽裡。 17 既然看見，就把天使論這孩子的話傳開了。 18 凡聽見的，就詫異牧羊之人對他們所說的話。 19 馬利亞卻把這一切的事存在心裡，反覆思想。 20 牧羊的人回去了，因所聽見、所看見的一切事正如天使向他們所說的，就歸榮耀於神，讚美他。

\newpage
%\subsection{Birth of Jesus (Luke 2:7-20) }%

\subsubsection{(Luke 2:7) }
Mary brought forth her firstborn Son, and wrapped Him in swaddling cloths, and laid Him in a manger, because there was no room for them in the inn.\\
\textbf{Where did Mary lay her firstborn Son? What was the name of this first born Son?}\\
\textbf{Why did Mary lay Jesus a manger?}\\

\subsubsection{(Luke 2:8-9) }
Now there were in the same country shepherds living out in the fields, keeping watch over their flock by night. 9 And behold, an angel of the Lord stood before them, and the glory of the Lord shone around them, and they were greatly afraid. \\
\textbf{Where did the angel of the Lord stand?}\\
\textbf{An angel of the Lord appeard to which kind of people?}\\
\textbf{What were the shepheres doing when an angel of the Lord appeard to them?}\\
\textbf{Why were the shepheres greatly afraid?}\\

\subsubsection{(Luke 2:10-12) }
10 Then the angel said to them, “Do not be afraid, for behold, I bring you good tidings (or news) of great joy which will be to all people. 11 For there is born to you this day in the city of David a Savior, who is Christ the Lord. 12 And this will be the sign to you: You will find a Babe wrapped in swaddling cloths, lying in a manger.”\\
\textbf{What kind of tidings (news) the angle brought to the shepheres}\\
\textbf{The good tidings is for:\hspace{1cm}  A, all the shepheres \hspace{1cm} B, all people}\\
\textbf{What is the identity of the new born Baby?}\\
\textbf{What is the sign of Christ the Lord?}\\

\subsubsection{(Luke 2:13-14) }
13 And suddenly there was with the angel a multitude of the heavenly host praising God and saying: 14 “Glory to God in the heavenly heights, Peace to all men and women on earth who please him!”\\
\textbf{Sunddenly, who appeared with the angel?}\\
\textbf{Filling the blanks: \hspace{1cm} Glory to}  \line(1,0){40} \hspace{1cm} \textbf{Peace to} \line(1,0){40}\\

\subsubsection{(Luke 2:15-16) }
So it was, when the angels had gone away from them into heaven, that the shepherds said to one another, “Let us now go to Bethlehem and see this thing that has come to pass, which the Lord has made known to us.” 16 And they came with haste and found Mary and Joseph, and the Babe lying in a manger. \\
\textbf{What did shepherds decide to do after the angels had gone away from them?}\\
\textbf{Following the angels instruction, what did they find ?}\\

\subsubsection{(Luke 2:17-18) }
17 Now when they had seen Him, they made widely known the saying which was told them concerning this Child. 18 And all those who heard it marveled at those things which were told them by the shepherds. \\
\textbf{In the statment of "Now when they had seen Him", Him refers to whom?}\\
\textbf{What did the shepherds do after they had seen Jesus?}\\
\textbf{We now had heard about Jesus, what we should learn from the shepherds?}\\
\textbf{What was the people's reaction after hearing the words of the shepherds?}\\

\subsubsection{(Luke 2:19-20) }
19 But Mary kept all these things and pondered them in her heart. 20 Then the shepherds returned, glorifying and praising God for all the things that they had heard and seen, as it was told them.\\
\textbf{What did Mary do after heard the words from the shepherds? What do we learn from Mary?}\\
\textbf{The shepherds glorified and praised God for what?}







