\chapter{耶稣受洗 Biptism (not teached)}

\section{罪人和罪犯的区别 Difference between Sin and crimical}

\section{罪的结局 God's attitude toward sin }

\section{罪的来源 Where did sin comes from}

\section{耶稣来的目的}
【约1:29】次日，约翰看见耶稣来到他那里，就说：“看哪，神的羔羊，除去世人罪孽的”\\

【John 1:29】The next day John saw Jesus coming toward him, and said, “Behold! The Lamb of God who takes away the sin of the world!\\


\section{施洗约翰预备道路}
\subsection{中文——太3:1-3/可1:4/約1:21-23/太3:5-6/太3:13-15}
【太 3:1-3】 那時，有施洗的約翰出來，在猶太的曠野傳道說： 2 「天國近了，你們應當悔改！」 3 這人就是先知以賽亞所說的，他說：「在曠野有人聲喊著說：『預備主的道，修直他的路！』」\\
【可1:4】 照这话，约翰来了，在旷野施洗，传悔改的洗礼，使罪得赦。\\
【約1:21-23】 他们又问他说：“这样，你是谁呢？是以利亚吗？”他说：“我不是。”“是那先知吗？”他回答说：“不是。” 22 于是他们说：“你到底是谁？叫我们好回复差我们来的人。你自己说你是谁？” 23 他说：“我就是那在旷野有人声喊着说：‘修直主的道路’，正如先知以赛亚所说的。”\\
【太 3:5-6】 那時，耶路撒冷和猶太全地並約旦河一帶地方的人，都出去到約翰那裡， 6 承認他們的罪，在約旦河裡受他的洗。\\
【太 3:13-15】 當下耶穌從加利利來到約旦河，見了約翰，要受他的洗。 14 約翰想要攔住他，說：「我當受你的洗，你反倒上我這裡來嗎？」 15 耶穌回答說：「你暫且許我，因為我們理當這樣盡諸般的義。」\\


\subsection{John the Baptist - Mathew 3:1-3/Mark 1:4/Johne 1:22-23/Mathew 3:5-6}
\textbf{Mathew 3:1-3} 1 In those days John the Baptist came, preaching in the wilderness of Judea, 2 and saying, “Repent, for the Kingdom of heaven has come near.” 3 This is he who was spoken of through the prophet Isaiah: “A voice of one calling in the wilderness, ‘Prepare the way for the Lord, make straight paths for him.’” \\
\textbf{Mark 1:4} And so John the Baptist appeared in the wilderness, preaching a baptism of repentance for the forgiveness of sins.\\
\textbf{Johne 1:22-23} Jews of Jerusalem said to John the Baptisthim, “Who are you?" John replied in the words of Isaiah the prophet, “I am the voice of one calling in the wilderness, ‘Make straight the way for the Lord.’”\\
\textbf{Mathew 3:5-6} People went out to him from Jerusalem and all Judea and the whole region of the Jordan. 6 Confessing their sins, they were baptized by him in the Jordan River.\\


\textbf{Where did John the Baptist give his preaching?}\\
\textbf{What is the message from John the Baptist?}\\
\textbf{When the "Kingdom of heaven" has come near, what did John the Baptist ask people to do?}\\
\textbf{The message of John the Baptist fulfilled which prophet's word?}\\
\textbf{What did isaiah prophecy?}\\
\textbf{John the Baptist prepare the way for whom}\\
\textbf{What blocks the way of the Lord?}\\
\textbf{Where is the way the Lord, or in another word: where is the way that John the Baptist prepared?}\\
\textbf{Who is the voice in the wilderness?}\\
\textbf{After John the Baptist prepared the way for the Lord, what was the reaction of the people?}\\
%\textbf{After John the Baptist prepared the way for the Lord, what was the reaction of the people?}\\
\textbf{What is the meaning of the baptism that John preached?}\\





