\chapter{Sin and Sinners 罪和罪人(Leo/Luna/Charlse/Micah/Luke/Luise)}
\section{什么是罪、罪人}
\subsection{中文-约1:29}

【羅馬書 1:18/28-32】 原來，神的憤怒從天上顯明在一切不虔不義的人身上，就是那些行不義阻擋真理的人。\\
他們既然故意不認識神，神就任憑他們存邪僻的心，行那些不合理的事： 29 裝滿了各樣不義、邪惡、貪婪、惡毒；滿心是嫉妒、凶殺、爭競、詭詐、毒恨； 30 又是讒毀的、背後說人的、怨恨神的、侮慢人的、狂傲的、自誇的、捏造惡事的、違背父母的、 31 無知的、背約的、無親情的、不憐憫人的。 32 他們雖知道神判定行這樣事的人是當死的，然而他們不但自己去行，還喜歡別人去行。\\
【創世記1:26-27】神說：「我們要照著我們的形象，按著我們的樣式造人，使他們管理海裡的魚、空中的鳥、地上的牲畜和全地，並地上所爬的一切昆蟲。」 27 神就照著自己的形象造人，乃是照著他的形象，造男造女。\\
【羅馬書 3:23】因为世人都犯了罪，亏缺了上帝的荣耀，\\
【赛53:5-8】 哪知他為我們的過犯受害，為我們的罪孽壓傷。因他受的刑罰我們得平安，因他受的鞭傷我們得醫治。 6 我們都如羊走迷，各人偏行己路，耶和華使我們眾人的罪孽都歸在他身上。7 他被欺壓，在受苦的時候卻不開口。 b他像羊羔被牽到宰殺之地，又像羊在剪毛的人手下無聲，他也是這樣不開口。 8 因受欺壓和審判，他被奪去，至於他同世的人，誰想他受鞭打，從活人之地被剪除，是因我百姓的罪過呢？\\
【約翰福音 1:1-4/12/29】太初有道，道與神同在，道就是神。 2 這道太初與神同在。 3 萬物是藉著他造的；凡被造的，沒有一樣不是藉著他造的。 4 生命在他裡頭，這生命就是人的光。12 凡接待他的，就是信他名的人，他就賜他們權柄做神的兒女。29 次日，約翰看見耶穌來到他那裡，就說：「看哪，神的羔羊，除去 世人罪孽的！


\subsection{英文 【Romans 1:18/28-32,3:23 Genesis 1:26-27 Isaiah 53:5-8】 teacher version}
【Romans 1:18】 For there is a revelation of the wrath of God from heaven against all the wrongdoing and evil thoughts of men who keep down what is true by wrongdoing;\\

\textbf{1 Who is God's wrath for? the wrath of god is revealed against which type of persons?}\\
\textbf{2 Does it include women and children?}\\

【Romans 1:28】 And because they had not the mind to keep God in their knowledge, God gave them up to an evil mind, to do those things which are not right;\\

\textbf{3 Why did God give them up to an evil mind to do those things which are not right?}\\
\textbf{4 What is the meaning of "gave them up to an evil mind"?}\\
\textbf{A） give them an evil mind\hspace{2cm}\\ B） surrendered/yielded up/entrusted/or transmitted to an evil mind\hspace{2cm}\\ C） forbidden them to have an evil mind}\\

【Romans 1:29-30】 Being full of all wrongdoing, evil, desire for the goods of others, hate, envy, putting to death, fighting, deceit, cruel ways, evil talk, and false statements about others;
Hated by God, full of pride, without respect, full of loud talk, given to evil inventions, not honouring father or mother.\\


\textbf{5 Can you list all the sins that commited by our heart or existed in our mind?}\\
\textbf{6 Are we a sinner according the law/judgement of God?}\\



【Romans 1:32】 They are stupid, unreliable, and don't have any love or pity for others. 32 They know God has said that anyone who acts this way deserves to die. But they keep on doing evil things, and they even encourage others to do them.\\

\textbf{7 What is the comment from God to these people?}\\
\textbf{8 Does the people know the law of God?}\\
\textbf{9 What is the fate of people who sinned against God's law?}\\
\textbf{10 What is the further more evil behavior when people doing wrong thing?}\\


【Genesis 1:26-27】 And God said, “We shall make men in our image, according to our form, and they shall rule among the fish of the Sea, and among the birds of Heaven, and among cattle, and among all animals of the Earth, and among all creepers that creep on the Earth.”\\
【Romans 3:23】 for all have sinned and fall short of the glory of God, \\

\textbf{11 Men are created according to whose image ?}\\
\textbf{12 After we have sinned, what is the consequence?}\\


【Isaiah 53:5-8】 5 He was wounded and crushed because of our sins; by taking our punishment, he made us completely well. 6 All of us were like sheep that had wandered off.  We had each gone our own way, but the LORD gave him the punishment we deserved. He was condemned to death without a fair trial. His life was taken away because of the sinful things my people had done.

\textbf{13 Why he was wounded and crushed?}\\
\textbf{14 What do we gain after taking our punishment?}\\
\textbf{15 While we had each gone our own waye, we have wandered off from whose way?}\\
\textbf{16 Who determined to give our punishment onto him?}\\
\textbf{17 What is our punishment he has taken for us?}\\

\textbf{\underline{bonus question} He was wounded and crushed, who is "He" ?}\\


【John 1:1-4/12/29】 4 In Jesus there was life, and that life was a light for the people of the world. 12 To all who did receive him, who believed in his name, he gave the right to become children of God, 29 The next day Jogn saw Jesus coming toward him, and said, “Behold, the Lamb of God, who takes away the sin of the world!\\

\textbf{18 Where was our life come from?}\\
\textbf{19 How to become the children of God?}\\
\textbf{20 Who is the Lamb of God?}\\
\textbf{21 Who determined to give our punishment onto him?}\\
\textbf{22 Why Jesus came to this world? or what is the task of Jesus coming to this world?}\\


\newpage
\subsection{student version}
\begin{itemize}
\item 【Romans 1:18】 For there is a revelation of the wrath of God from heaven against all the wrongdoing and evil thoughts of men who keep down what is true by wrongdoing;\\


\item 【Romans 1:28】 And because they had not the mind to keep God in their knowledge, God gave them up to an evil mind, to do those things which are not right;\\


\item 【Romans 1:29-30】 Being full of all wrongdoing, evil, desire for the goods of others, hate, envy, putting to death, fighting, deceit, cruel ways, evil talk, and false statements about others;
Hated by God, full of pride, without respect, full of loud talk, given to evil inventions, not honouring father or mother.\\



\item 【Romans 1:32】 They are stupid, unreliable, and don't have any love or pity for others. 32 They know God has said that anyone who acts this way deserves to die. But they keep on doing evil things, and they even encourage others to do them.\\


\item 【Genesis 1:26-27】 And God said, “We shall make men in our image, according to our form, and they shall rule among the fish of the Sea, and among the birds of Heaven, and among cattle, and among all animals of the Earth, and among all creepers that creep on the Earth.”\\
【Romans 3:23】 for all have sinned and fall short of the glory of God, \\

\item 【Isaiah 53:5-8】 5 He was wounded and crushed because of our sins; by taking our punishment, he made us completely well. 6 All of us were like sheep that had wandered off.  We had each gone our own way, but the LORD gave him the punishment we deserved. He was condemned to death without a fair trial. His life was taken away because of the sinful things my people had done.


\item 【John 1:1-4/12/29】  4 In Jesus there was life, and that life was a light for the people of the world. 12 To all who did receive him, who believed in his name, he gave the right to become children of God, 29 The next day Jogn saw Jesus coming toward him, and said, “Behold, the Lamb of God, who takes away the sin of the world!

\end{itemize}

%\textbf{\underline{bonus question} He was wounded and crushed, who is "He" ?}\\


